Observing and Predicting Knowledge Worker Stress, Focus and Awakeness in the Wild

### 2020-10-12 IJHCSSubmission/bp_results_1.tex
minor last revisions

\begin{table}[]
    \centering
\rev{\begin{tabularx}{\textwidth}{|c|c c c|c c c|}
    \hline
        &
        \multicolumn{3}{c|}{Stress} & 
        \multicolumn{3}{c|}{Awakeness} \\
        \hline
        \textbf{Variable} & \centering
        \textbf{\rev{F.E.E.}}& \textbf{p-value} & \textbf{\rev{C.I. (95\%)}} & \centering \textbf{\rev{F.E.E.}}  & \textbf{p-value} & \textbf{\rev{C.I. (95\%)}}\\
        \hline
        Monday & \centering -0.033 & 0.745 & \rev{$(-0.234, 0.167)$} & \centering -0.058 & 0.497 & \rev{$(-0.227, 0.110)$}\\
        Tuesday & \centering 0.028 & 0.773 & \rev{$(-0.164, 0.221)$} & \centering 0.036 & 0.662 & \rev{$(-0.126, 0.198)$}\\
        Wednesday & \centering 0.163 & 0.100 & \rev{$(-0.031, 0.357)$} & \centering -0.018 & 0.830 & \rev{$(-0.181, 0.145)$}\\
        Thursday & \centering 0.022 & 0.821 & \rev{$(-0.169, 0.213)$} & \centering 0.076 & 0.927 & \rev{$(-0.085, 0.238)$}\\
        Friday & \centering 0.082 & 0.473 & \rev{$(-0.142, 0.306)$} & \centering -0.178 & 0.025 & \rev{$(-0.334, -0.022)$}\\
        Month End & \centering 0.044 & 0.687 & \rev{$(-0.171, 0.259)$} & \centering -0.082 & 0.374 & \rev{$(-0.263, 0.099)$}\\
        \hline
    \end{tabularx}
    \caption{\rev{Fixed effects estimates (F.E.E.), 95\% confidence intervals and associated p-values for the explanatory variables (day of week and proximity to month end) that we examined in our linear mixed model analysis.}}    \label{tab:mixedModel}}
\end{table}

>>>>

\begin{table}[]
    \centering
\rev{\begin{tabularx}{\textwidth}{|c|c c c|c c c|}
    \hline
        &
        \multicolumn{3}{c|}{Stress} & 
        \multicolumn{3}{c|}{Awakeness} \\
        \hline
        \textbf{Variable} & \centering
        \textbf{\rev{F.E.E.}}& \textbf{p-value} & \textbf{\rev{C.I. (95\%)}} & \centering \textbf{\rev{F.E.E.}}  & \textbf{p-value} & \textbf{\rev{C.I. (95\%)}}\\
        \hline
        Monday & \centering -0.033 & 0.745 & \rev{$(-0.234, 0.167)$} & \centering -0.058 & 0.497 & \rev{$(-0.227, 0.110)$}\\
        Tuesday & \centering 0.028 & 0.773 & \rev{$(-0.164, 0.221)$} & \centering 0.036 & 0.662 & \rev{$(-0.126, 0.198)$}\\
        Wednesday & \centering 0.163 & 0.100 & \rev{$(-0.031, 0.357)$} & \centering -0.018 & 0.830 & \rev{$(-0.181, 0.145)$}\\
        Thursday & \centering 0.022 & 0.821 & \rev{$(-0.169, 0.213)$} & \centering 0.076 & 0.927 & \rev{$(-0.085, 0.238)$}\\
        Friday & \centering 0.082 & 0.473 & \rev{$(-0.142, 0.306)$} & \centering -0.178 & 0.025 & \rev{$(-0.334, -0.022)$}\\
        Month End & \centering 0.044 & 0.687 & \rev{$(-0.171, 0.259)$} & \centering -0.082 & 0.374 & \rev{$(-0.263, 0.099)$}\\
        \hline
    \end{tabularx}
    \caption{\rev{Fixed effects estimates (F.E.E.), 95\% confidence intervals (C.I.) and associated p-values for the explanatory variables (day of week and proximity to month end) that we examined in our linear mixed model analysis.}}    \label{tab:mixedModel}}
\end{table}
